Comparative study of requantization of time-dependent mean-field for pairing dynamics

### 2017-10-06 draft1.1.tex
added some figures

\subsubsection{Periodic boundary condition}

@@

\subsubsection{Adiabatic approximation}
We assume $j$ as a coordinate, $\phi$ as a conjugate momentum. 
The adiabatic approximation means $\phi$ in Hamiltonian can be
 expanded up to second order
\begin{align}
 \mathcal{H}(\phi,j;J)
	\approx V(j:J) + \frac{1}{2B(j;J)}j^2
\end{align}
where
\begin{align}
 V(j:J) &\equiv \mathcal{H}(\phi=0,j;J) \nonumber \\
  &= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l(1- q_l)
	- \frac{g}{4} (\Omega_l(1-q_l^2)+(1-q_l)^2) \right\}
- \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} \\
 B(j;J)^{-1} &\equiv \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2}\right|_{\phi=0} \nonumber \\
 &= \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} .
\end{align}
We transform the carved space into plain space
 which keeps the mass parameter equals one
\begin{align}
 \mathcal{H}(\phi,j;J) \to \mathcal{\bar{H}}(p,q;J) = \bar{V}(q;J) + \frac{1}{2}p^2 .
\end{align}
The relation between both coordinates fulfills
\begin{align}
 \frac{\partial q(j)}{\partial j} = \sqrt{B(j;J)} .
\end{align}
Instead of Pauli prescription, we solve the Schr\"{o}dinger equation in plain space
\begin{equation}
	\bar{H}\left( q,-i\frac{d}{dq},\frac{N}{2} \right)
	u_k^{(N)}(q) = E_k^{(N)}u_k^{(N)}(q).
	\label{Schroedinger_eq2}
\end{equation}
At weak pairing limit in ground state, most of the component of wave function is expected to occupy around the minimum value of $j$. We choose Neumann boundary condition $u_k^{(N)}(q)'|_{q=q_{min}}=0$, where $q_{min}$ corresponds to the minimum value of $j$.

@@

We apply the requantization methods in Sec.~\ref{sec:requantization}.
In the following, the stationary-phase approximation to the path
integral in Sec.~\ref{sec:SPA} is denoted as ``SPA'',
the Fourier decomposition method (Sec.~\ref{sec:Fourier}) as ``FD'',
and the canonical quantization (Sec.~\ref{sec:canonical}) as ``CQ''.
In addition, the harmonic approximation at the ground state is
called ''HA''.
Note that the SPA and the FD produce the same eigenenergies which
are based on the EBK quantization rule.

@@

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ_woType2.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ_woType2.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-12.5$ corresponds to 0p50h configuration, $-11.5$ corresponds to 2p52h configuration, and so on.}
 \label{fig:N50_occ}
\end{figure}

@@

@@

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ_woType2.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ_woType2.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=8$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-2$ corresponds to 0p8h configuration, $-1$ corresponds to 2p10h configuration, and so on.}
 \label{fig:N8_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ_woType2.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
%  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ_woType2.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-4$ corresponds to 0p0h configuration, $-3$ corresponds to 2p2h configuration, and so on.}
 \label{fig:N16_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=45mm,angle=-90]{images/N8p_Delta.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=8$ system.}
 \label{fig:p_Delta1}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=45mm,angle=-90]{images/N16p_Delta.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=16$ system.}
 \label{fig:p_Delta2}
\end{figure}

>>>>

\subsubsection{Periodic boundary condition}
\label{subsec:canonical1}

@@

\subsubsection{Adiabatic approximation}
\label{subsec:canonical2}

We assume $j$ as a coordinate, $\phi$ as a conjugate momentum. 
The adiabatic approximation means $\phi$ in Hamiltonian can be
 expanded up to second order
\begin{align}
 \mathcal{H}(\phi,j;J)
	\approx V(j:J) + \frac{1}{2B(j;J)}j^2
\end{align}
where
\begin{align}
 V(j:J) &\equiv \mathcal{H}(\phi=0,j;J) \nonumber \\
  &= \sum_{l=1,2} \Omega_l \left\{ \epsilon_l(1- q_l)
	- \frac{g}{4} (\Omega_l(1-q_l^2)+(1-q_l)^2) \right\}
- \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} \\
 B(j;J)^{-1} &\equiv \left. \frac{\partial^2\mathcal{H}}{\partial\phi^2}\right|_{\phi=0} \nonumber \\
 &= \frac{g}{2}\Omega_1\Omega_2
	\sqrt{(1-q_1^2)(1-q_2^2)} .
\end{align}
We transform the carved space into plain space
 which keeps the mass parameter equals one
\begin{align}
 \mathcal{H}(\phi,j;J) \to \mathcal{\bar{H}}(p,q;J) = \bar{V}(q;J) + \frac{1}{2}p^2 .
\end{align}
The relation between both coordinates fulfills
\begin{align}
 \frac{\partial q(j)}{\partial j} = \sqrt{B(j;J)} .
\end{align}
Instead of Pauli prescription, we solve the Schr\"{o}dinger equation in plain space
\begin{equation}
	\bar{H}\left( q,-i\frac{d}{dq},\frac{N}{2} \right)
	u_k^{(N)}(q) = E_k^{(N)}u_k^{(N)}(q).
	\label{Schroedinger_eq2}
\end{equation}
At weak pairing limit in ground state, most of the component of wave function is expected to occupy around the minimum value of $j$. We choose Neumann boundary condition $u_k^{(N)}(q)'|_{q=q_{min}}=0$, where $q_{min}$ corresponds to the minimum value of $j$.

@@

We apply the requantization methods in Sec.~\ref{sec:requantization}.
In the following, the stationary-phase approximation to the path
integral in Sec.~\ref{sec:SPA} is denoted as ``SPA'',
the Fourier decomposition method (Sec.~\ref{sec:Fourier}) as ``FD'',
 the canonical quantization with periodic boundary condition 
(Sec.~\ref{subsec:canonical1}) as ``CQ1'', and the canonical quantization 
with adiabatic approximation (Sec.~\ref{subsec:canonical2})  as ``CQ2''.
In addition, the harmonic approximation at the ground state is
called ''HA''.
Note that the SPA and the FD produce the same eigenenergies which
are based on the EBK quantization rule.

@@

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N50Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N50Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-12.5$ corresponds to 0p50h configuration, $-11.5$ corresponds to 2p52h configuration, and so on.}
 \label{fig:N50_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
%  \includegraphics[width=60mm,angle=-90]{images/N100ex_energy.eps}
 \end{center}
 \caption{Excitation energies of $\ket{0_2^+}$, $\ket{0_3^+}$ and $\ket{0_4^+}$ in $N=50$ system.}
 \label{fig:N50energy}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N100Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N100Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-12.5$ corresponds to 0p50h configuration, $-11.5$ corresponds to 2p52h configuration, and so on.}
 \label{fig:N50_occ}
\end{figure}

\begin{figure}[htbp]
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_exact.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_Type1.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \begin{minipage}{0.33\hsize}
 \begin{center}
%  \includegraphics[width=70mm,angle=-90]{images/N100Pad_semiclassical.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
 \end{minipage}
 \caption{The strength of pair additional transition from $N=48$ to $N=50$ system defined in (\ref{Pad}). The results of $\ket{0_1^+}\to\ket{0_1^+}$, $\ket{0_1^+}\to\ket{0_2^+}$, $\ket{0_2^+}\to\ket{0_1^+}$ and $\ket{0_2^+}\to\ket{0_2^+}$ are shown. Left panels: exact solution; Middle panels: canonical quantization; Right panels: semiclassical approach.}
 \label{fig:N50Pad}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N8Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N8Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=8$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-2$ corresponds to 0p8h configuration, $-1$ corresponds to 2p10h configuration, and so on.}
 \label{fig:N8_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N16Xeq0p5occ.eps}
 \end{center}
 \end{minipage}
 \begin{minipage}{1\hsize}
 \begin{center}
  \includegraphics[width=67mm,angle=-90]{images/N16Xeq2occ.eps}
 \end{center}
 \end{minipage}
 \caption{Occupation probability in excited $0^+$ states as a function of $\pi$ in $N=50$ system. The upper and lower panels display the results for $x=0.05$ and $x=0.2$, respectively. From the physical meaning of $\pi$, $-4$ corresponds to 0p0h configuration, $-3$ corresponds to 2p2h configuration, and so on.}
 \label{fig:N16_occ}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=50mm,angle=-90]{images/N8p_E.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=8$ system.}
 \label{fig:p_Delta1}
\end{figure}

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=50mm,angle=-90]{images/N16p_E.eps}
 \end{center}
 \caption{Pairing gap $\Delta$ in (\ref{Delta_BCS}) as a function of $\pi$ with various pairing strength in $N=16$ system.}
 \label{fig:p_Delta2}
\end{figure}
